Verifying Demonstrations

### 2019-02-28 paper/privacy-analysis.tex

However, there are more data than \(\pid, \wid\) used in the protocol.
The protocol uses \(\cid, \pid, \wid, t_s, t_s', l, \corr_\pid, \corr_\wid\).
We assume that the \(\cid\) will be used by many individuals, as it is the 
cause identifier.
And thus it cannot be used to uniquely identity any individual.

We assume that the location \(l\) is coarse enough so that many non-overlapping 
\((\pid, \wid)\)-pairs use the same location.
After all, it is the location of the protest, not the location within the 
protest that is interesting.
Thus \(l\) is not uniquely identifying any individual protester or witness.
Likewise, thanks to the constraints in the time-stamp granularity 
(\cref{timestamp}), \(t\) is not uniquely identifying either.

>>>>

However, there are more data than \(\pid, \wid\) used in the protocol.
The protocol uses \(\cid, \pid, \wid, t_s, t_s', l, \corr_\pid, \corr_\wid\).
The cause identifier \(\cid\) will be used for all proof shares
pertaining to the same protest and thus it cannot be used to uniquely
identify any individual. The location \(l\) is coarse enough so that many non-overlapping 
\((\pid, \wid)\)-pairs use the same location.
After all, it is the location of the protest, not the location within the 
protest that matters.
Thus \(l\) is not uniquely identifying any individual protester or witness.
Likewise, thanks to the constraints in the time-stamp granularity 
(\cref{timestamp}), \(t\) is not uniquely identifying either.

### 2019-02-28 paper/protocol.tex

The entities involved in our protocol are participants and (count) verifiers.

A participant is an individual who wants to participate in a given 
protest.
A participant can assume three different roles:
\begin{enumerate}
\item The \emph{organizer} has written a manifesto (at minimum a name) for the protest and 
  disseminated it to others.
\item A \emph{protester} is attending the protest and asks witnesses to vouch 
  for their presence.
\item A \emph{witness} provides proofs to protesters which state that the 
  protester was indeed participating, constructed such that the proofs are verifiable by 
  third parties.
\end{enumerate}
In general, there is one organizer and every participant can act as
either or both protester and witness.

@@

\emph{Registration: \(\sk\gets 
    \Proto{\CROCUSreg[_P][\spk]}{\CROCUSreg[_{\CA}][\ssk]}\).}
During the registration phase, each participant generates a secret key~\((k, 
  r)\) and obtains a signature on it by the \ac{CA} \emph{but without revealing 
  it} to the \ac{CA}.
At the end, each participant will have a signed secret key while the \ac{CA} 
will issue only one signature per participant but without knowing the 
association between a particular key and the identity of the participant.
The participant chooses \(k, r\rgets \ZZ_q\) uniformly randomly and runs 
\(\sigma \gets \Proto{\ACgetSig[\spk, k, r]}{\ACissueSig[\spk, \ssk]}\) (see 
\cref{ACacAlg}).
Upon success, the participant sets \(\sk = (\sigma, k, r)\).

@@

\emph{Creation of a protest: the manifesto.}
The organizer writes a manifesto for the protest, which describes its cause.
This manifesto could take the form of any intelligible text.
The organizer will then distribute this manifesto to people through
any suitable means  (\eg on the Web, on placards, \etc).
If they agree with the cause, they will use the knowledge of the
manifesto to join the protest.

\emph{Joining as a protester: \((\pid, t_s)\gets 
    \CROCUSjoin[_P][\text{manifesto}]\).}
A protester who wants to join the protest will use the manifesto to
compute an identifier for the cause by hashing the manifesto,
\(\cid\gets \Hash[\mfst]\) (and comparing the result to that received
from the organizer, we omit this in the protocol for readibility).
Afterwards, this identifier is used to create the protest-specific identifier 
for the protester, \(\pid\gets \ACprf[_{\sk_P}][\cid]\)%
% (see \cref{fig:ProofFig} and \cref{ACprfAlg} in the appendix for details of 
%the algorithms)%
.
The protester should also fetch a time-correlated random value, \(t_s\), from 
\(\TS\), \(t_s\gets \TSget\).

\emph{Joining as a witness: \(t_s'\gets \CROCUSjoin_W\).}
The witness should simply get a time-correlated random value from the time-stamping service, \(t_s'\gets \TSget\).
Note that we do this for redundancy, the newest of \(t_s\) and \(t_s'\) will 
set the start of the time interval of creation for the proof share.

@@

\emph{Submission: \(\psh_W\gets \CROCUSsubmit[_W][\cid, \pid, \wid, t_s, t_s', 
    l]\).}
The witness should, just as the protester, commit the proof-share data to the 
ledger, \(t_e\gets \TSsubmit[\Hash[\cid, \pid, \wid, t_s, t_s', l]]\).
%(This is to make the time interval as early as possible, whoever is the faster 
%will submit it.) \sonja{but both do}
Then, without any time requirements, the witness computes \iac{NIZK} proof 
\(\corr_{\wid}\) as follows:
\begin{multline*}
  \corr_{\wid}\gets \SPK\left\{ (\sk_W) : \right. \\
    \begin{aligned}
      \wid &= \ACprf[_{\sk_W}][\pid] \quad \land \\
      \sigma_W' &= \left. \ACblind[\ACsign[_{\ssk}][\sk_W]] \right\}
    \end{aligned} \\
      (\cid, \pid, \wid, t_s, t_s', l).
\end{multline*}
Finally, the witness uploads the tuple \[
  \psh_W = (\cid, \pid, \wid, t_s, t_s', t_e', l, \corr_{\wid})
\] for permanent storage on the ledger, \(\TSsubmit[\psh_W]\).

@@

Then the set of all valid proof shares for a protester \(j\) constitutes its 
participation proof \(\prf_{j}\), as in \cref{DefParticipationProof},
and the verifier thus can derive the set of \((\str,\theta)\)-eligible participation proofs \(\prfs_{\prtst}^{\str,\theta}\) for all protesters for the protest \(\prtst\), as in \cref{DefParticipationCount}.
Finally, the  participation count \(|\prfs_{\prtst}^{\str,\theta}|\) is the cardinality of this set by the same \cref{DefParticipationCount}.

@@

In the case of trusted witnesses, each such trusted witness must
publish or otherwise inform the verifier of which proof shares they
have signed, \eg by giving a list of all such proof shares or
digitally signing each proof share\footnote{%
  To achieve witness privacy in this situation, one could employ a
  group or ring signature scheme for a set of trusted witnesses, \eg
  members of an independent journalist association.  Then one learns
  that at least one member of this set of trusted witnesses must have
  been there.
}.

>>>>

The entities involved in our protocol are participants and (count) verifiers.
A participant can assume three different roles:
\begin{enumerate}
\item The \emph{organizer} has written a manifesto for the protest and 
  disseminated it to others.
\item A \emph{protester} is attending the protest and asks witnesses to vouch 
  for their presence.
\item A \emph{witness} provides proofs to protesters which state that they indeed participated, constructed such that the proofs are verifiable by 
  third parties.
\end{enumerate}
In general, there is one organizer and every participant can act as
either or both protester and witness.

@@

\emph{Registration: \(\sk\gets 
    \Proto{\CROCUSreg[_P][\spk]}{\CROCUSreg[_{\CA}][\ssk]}\).}
During the registration phase, each participant generates a secret key~\((k, 
  r)\) and obtains a signature on it by the \ac{CA} \emph{but without revealing 
  it} to the \ac{CA} (or to any part thereof in a multi-party scenario).
At the end, each participant will have a signed secret key while the \ac{CA} 
will issue only one signature per participant but without knowing the 
association between a particular key and the identity of the participant.
The participant chooses \(k, r\rgets \ZZ_q\) uniformly randomly and runs 
\(\sigma \gets \Proto{\ACgetSig[\spk, k, r]}{\ACissueSig[\spk, \ssk]}\) (see 
\cref{ACacAlg}).
Upon success, the participant sets \(\sk = (\sigma, k, r)\).

@@

\emph{Creation of a protest: the manifesto.}
The organizer writes a manifesto for the protest, which describes its cause.
This manifesto could take the form of any intelligible text, in
practice at minimum a name.
The organizer then distributes this manifesto to people through
any suitable means  (\eg on the Web, on placards, \etc).
If they agree with the cause, they will use the knowledge of the
manifesto to join the protest.

\emph{Joining as a protester: \((\pid, t_s)\gets 
    \CROCUSjoin[_P][\text{manifesto}]\).}
A protester who wants to join the protest uses the manifesto to
compute an identifier for the cause by hashing the manifesto,
\(\cid\gets \Hash[\mfst]\) (and comparing the result to that received
from the organizer, we omit this in the protocol for readibility).
Afterwards, this identifier is used to create the protest-specific identifier 
for the protester, \(\pid\gets \ACprf[_{\sk_P}][\cid]\)%
% (see \cref{fig:ProofFig} and \cref{ACprfAlg} in the appendix for details of 
%the algorithms)%
.
The protester also fetches a time-correlated random value, \(t_s\), from 
\(\TS\), \(t_s\gets \TSget\).

\emph{Joining as a witness: \(t_s'\gets \CROCUSjoin_W\).}
The witness simply gets a time-correlated random value from the time-stamping service, \(t_s'\gets \TSget\).
Note that we do this for redundancy, the newest of \(t_s\) and \(t_s'\) will 
set the start of the time interval of creation for the proof share.

@@

\emph{Submission: \(\psh_W\gets \CROCUSsubmit[_W][\cid, \pid, \wid, t_s, t_s', 
    l]\).}
The witness, like the protester, commits the proof-share data to the 
ledger, \(t_e\gets \TSsubmit[\Hash[\cid, \pid, \wid, t_s, t_s', l]]\).
%(This is to make the time interval as early as possible, whoever is the faster 
%will submit it.) \sonja{but both do}
Then, without any time requirements, the witness computes \iac{NIZK} proof 
\(\corr_{\wid}\) as follows:
\begin{multline*}
  \corr_{\wid}\gets \SPK\left\{ (\sk_W) : \right. \\
    \begin{aligned}
      \wid &= \ACprf[_{\sk_W}][\pid] \quad \land \\
      \sigma_W' &= \left. \ACblind[\ACsign[_{\ssk}][\sk_W]] \right\}
    \end{aligned} \\
      (\cid, \pid, \wid, t_s, t_s', l).
\end{multline*}
Finally, the witness uploads the tuple \[
  \psh_W = (\cid, \pid, \wid, t_s, t_s', t_e', l, \corr_{\wid})
\] for permanent storage on the ledger, \(\TSsubmit[\psh_W]\).

@@

Then the set of all valid proof shares for a protester \(j\) constitutes its 
participation proof \(\prf_{j}\), as in \cref{DefParticipationProof},
and the verifier thus can derive the set of \((\str,\theta)\)-eligible participation proofs \(\prfs_{\prtst}^{\str,\theta}\) for all protesters for the protest \(\prtst\), as in \cref{DefParticipationCount}.
Finally, the  participation count \(|\prfs_{\prtst}^{\str,\theta}|\) is the cardinality of this set by  \cref{DefParticipationCount}.

@@

In the case of trusted witnesses, each such trusted witness must
publish or otherwise inform the verifier of which proof shares they
have signed, \eg by giving a list of all such proof shares or
digitally signing each proof share\footnote{%
  To achieve witness privacy in this situation, one could employ a
  group or ring signature scheme for a set of potentially trusted witnesses, \eg
  members of an independent journalist association.  Then one learns
  that at least one member of this set must have
  been there.
}.
